Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2022-01-29 FDT2020/Introduction.tex
adrresed the choice

@@

For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multi-edges allowed. A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.  An IP formulation for this problem, known as the {\em subtour-elimination}, is
 \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in \{0,1,2\}^{E}\}, 
 \label{eq:subtour}
 \end{equation}
where $\delta(U)$ for vertex subset $U$ is the set of edges that cross the cut defined by $U$.  That is, each $e \in \delta(U)$ has one endpoint in $U$ and the other endpoint in $V-U$. We denote the linear relaxation of this IP as $\subtour(G)$. Notice that in this case, $G$ defines the polyhedron, while the pair of $G$ and $c$ defines the instance of 2EC. Let $I_G$ be the polyhedron instance defined by $\subtour(G)$. Then $g(I_G)$ is the worst-case integrality gap 2EC on $G$ over all non-negative cost functions and integrality gap of 2EC is $\max_{G} g(I_G))$.

>>>>

The reason that we define integrality gap for a polyhedron as opposed to an instance of a problem is that our algorithms are independent of the cost function $c$.

@@

For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multi-edges allowed. A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.  An IP formulation for this problem, known as the {\em subtour-elimination}, is
 \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in \{0,1,2\}^{E}\}, 
 \label{eq:subtour}
 \end{equation}
where $\delta(U)$ for vertex subset $U$ is the set of edges that cross the cut defined by $U$.  That is, each $e \in \delta(U)$ has one endpoint in $U$ and the other endpoint in $V-U$. We denote the linear relaxation of this IP as $\subtour(G)$. Notice that in this case, $G$ defines the polyhedron, while the pair of $G$ and $c$ defines the instance of 2EC. Let $I_G$ be the polyhedron instance defined by $\subtour(G)$. Then $g(I_G)$ is the worst-case integrality gap 2EC on $G$ over all non-negative cost functions and integrality gap of 2EC is $\sup_{G} g(I_G)$.
